%-------------------------
% Resume in Latex Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = *}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
\usepackage[sfdefault]{FiraSans}
\usepackage[sfdefault]{roboto}
\usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}

% serif
\usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Nilton Moura} \\ \vspace{1pt}
    \small +XX XX XXX-XXX-XXX $|$ \href{mailto:xyz@xyz.com}{\underline{xyz@xyz.com}} $|$ 
    \href{https://linkedin.com/in/nmoura}{\underline{linkedin.com/in/nmoura}} $|$
    \href{https://github.com/nmoura}{\underline{github.com/nmoura}}
\end{center}

\section{Summary}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        \textbf{}{Senior Engineer with 17+ years of experience mostly in tech industry in Brazil and abroad. Specializes in Linux systems, networking and programming. At AWS in Ireland, designed and developed a network discovery system that mapped highly restricted networks, helping eliminate an L2 architectural bottleneck affecting all AWS datacenters by enabling a transition to a scalable L3 design. Also developed the CLI for a new terminal-server hardware designed within the team and contributed to its Linux-based operating system using Buildroot.}
      }}
 \end{itemize}
  
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Head of Technology}{Jun 2022 -- Nov 2025}
      {SAF Botafogo}{Rio de Janeiro, Brazil}
      \resumeItemListStart
        \resumeItem{Built the department from the ground up, growing it from 0 to 8 people and delivering infrastructure, systems, and data projects supporting 300+ users.}
        \resumeItem{Leads and sponsors initiatives such as datacenter retrofit, Wi-Fi for 30k fans, data lake/warehouse developed by the team, which provided geospatial insights that enabled marketing to choose the location of a new physical store within minutes.}
        \resumeItem{Mentors the members of the team in technical, behavioral and career matters in weekly 1:1 meetings.}
        \resumeItem{Partners with all departments to align technology initiatives with business strategy.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Senior Systems Management Specialist}{Jul 2021 -- Jun 2022}
      {Kyndryl}{Rio de Janeiro, Brazil}
      \resumeItemListStart
        \resumeItem{Managed RHEL servers running IBM's Wall Street Systems with Ansible, Python and Shellscripts.}
        \resumeItem{Provided customer-facing support on highly complex issues and participated in on-call rotation.}
        \resumeItem{Mentored other engineers in Python.}
    \resumeItemListEnd

    \resumeSubheading
      {Systems Development Engineer II}{Sep 2018 -- May 2021}
      {Amazon Web Services}{Dublin, Ireland}
      \resumeItemListStart
        \resumeItem{Created, developed and maintained a network discovery system that mapped large networks in restricted environments. The system gave Network Engineers visibility into the Console Network (RS-232) for the first time, enabling migration from a legacy Layer 2 to a scalable Layer 3 design.}
        \resumeItem{Participated in building a Linux Buildroot-based operating system for a new terminal-server hardware, also developing its CLI (Command Line Interface).}
        \resumeItem{Developed automation tools in Python to rotate credentials and orchestrate network-migration tasks, reducing manual errors and cutting region-wide credential rotation from days to hours, and individual DC fabric migrations from 5 to 2 days.}
      \resumeItemListEnd

    \resumeSubheading
      {Senior Support Analyst}{Mar 2017 -- Aug 2018}
      {ANBIMA, Brazil's Central Bank}{Rio de Janeiro, Brazil}
      \resumeItemListStart
        \resumeItem{Designed and implemented JBoss and Apache servers on RHEL using Ansible, applying best security practices from CIS (Center for Internet Security) for an application to serve account statement of big financial players on Internet, with all components (databases, web and middleware servers) with mutual authentication and all traffic encrypted.}
        \resumeItem{Led a project of Dynatrace (Application Performance Management) software implementation.}
        \resumeItem{Troubleshooted high complexity issues.}
      \resumeItemListEnd

    \resumeSubSubheading
     {Support Analyst}{Jul 2014 - Feb 2017}
     \resumeItemListStart
       \resumeItem{Wrote a standard document for shell scripts' development of the site disaster recovery automation. Developed standardized functions to be consumed by the shell scripts developed for the automated DR. Later, orchestrated the execution of those scripts using Jenkins Pipeline. This reduced the time for the exchange of roles between sites from ~4h to 16m during DR exercises.}
       \resumeItem{Designed and implemented a new architecture for 40 JBoss EAP instances; in the old architecture, there were 4 instances with around 10 applications each.}
       \resumeItem{Implemented GitLab for infrastructure teams and gave Git and GitLab basic lessons to colleagues.}
       \resumeItem{Supported the development teams in JBoss EAP 6 and CI/CD tools like Jenkins, Sonar and Selenium.}
     \resumeItemListEnd

    \resumeSubheading
      {IT Analyst}{Jan 2011 -- Jul 2014}
      {Petrobras, by Spassu Tecnologia}{Rio de Janeiro, Brazil}
      \resumeItemListStart
        \resumeItem{Supported development teams in JBoss EAP 5 and 6, CI process with Jenkins, Sonar, JIRA, Git, Subversion and Mercurial in RHEL and CentOS.}
        \resumeItem{Designed and implemented the JBoss EAP 6 architecture and Spacewalk for all Brazil E\&P workstations and servers, based on RHEL and CentOS, automatizing Red Hat channels synchronization with Python.}
        \resumeItem{Implemented a GitLab server for development and infrastructure teams.}
        \resumeItem{Wrote a baseline for the VMWare virtual servers, for RHEL 6 and CentOS.}
        \resumeItem{Implemented Jenkins and applications deployment with shell scripts.}
        \resumeItem{Began the implementation of Puppet Open Source for servers and workstations configuration management.}
      \resumeItemListEnd

    \resumeSubheading
      {Senior Support Analyst}{May 2010 -- Dec 2010}
      {Equinix Brasil}{Rio de Janeiro, Brazil}
      \resumeItemListStart
        \resumeItem{Identified root causes of recurrent issues. Troubleshooted high complexity issues, mainly in Linux and its services. Supported analysts on technical matters.}
      \resumeItemListEnd

    \resumeSubSubheading
     {Junior Support Analyst}{Aug 2009 - May 2010}
     \resumeItemListStart
       \resumeItem{Treated issues quickly enough to try to avoid breaking up SLA as first customer contact, mainly in Linux systems and its services like DNS (BIND), Web (Apache), Database (MySQL), Email (Postfix and Zimbra), Firewall (iptables), Proxy (Squid) and Shellscript.}
     \resumeItemListEnd

    \resumeSubheading
      {Operations Analyst}{Dec 2008 -- Jul 2009}
      {AMT Internet Security \& Datacenter}{Rio de Janeiro, Brazil}
      \resumeItemListStart
        \resumeItem{Responsible for design, deploy and server management, mostly in Linux environments for services like DNS (BIND and Windows 2008), Firewall (iptables), Antispam, Monitoring (Nagios), in physical and virtual servers (Citrix-Xen), providing customer-facing last level support.}
      \resumeItemListEnd

    \resumeSubSubheading
     {Junior Support Analyst}{Sep 2008 - Nov 2008}
     \resumeItemListStart
       \resumeItem{Monitored servers and services, being the customer's first point of contact.}
     \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Gama Filho University}{Rio de Janeiro, RJ}
      {Tech. Degree in Computer Networks; GPA: 8.8/10, equivalent to 3.5/4.0}{Feb. 2009 -- Feb 2012}
    \resumeSubheading
      {Colégio Nacional}{Rio de Janeiro, RJ}
      {High School Degree specialized in IT}{Feb. 1998 -- Jul 2001}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
%\section{Projects}
%    \resumeSubHeadingListStart
%      \resumeProjectHeading
%          {\textbf{Gitlytics} $|$ \emph{Python, Flask, React, PostgreSQL, Docker}}{June 2020 -- Present}
%          \resumeItemListStart
%            \resumeItem{Developed a full-stack web application using with Flask serving a REST API with React as the frontend}
%            \resumeItem{Implemented GitHub OAuth to get data from user’s repositories}
%            \resumeItem{Visualized GitHub data to show collaboration}
%            \resumeItem{Used Celery and Redis for asynchronous tasks}
%          \resumeItemListEnd
%      \resumeProjectHeading
%          {\textbf{Simple Paintball} $|$ \emph{Spigot API, Java, Maven, TravisCI, Git}}{May 2018 -- May 2020}
%          \resumeItemListStart
%            \resumeItem{Developed a Minecraft server plugin to entertain kids during free time for a previous job}
%            \resumeItem{Published plugin to websites gaining 2K+ downloads and an average 4.5/5-star review}
%            \resumeItem{Implemented continuous delivery using TravisCI to build the plugin upon new a release}
%            \resumeItem{Collaborated with Minecraft server administrators to suggest features and get feedback about the plugin}
%          \resumeItemListEnd
%    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Main Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Core Skills}{: Linux, Python, Bash, Networking } \\
     \textbf{Tools}{: Git, Jenkins, Ansible, Docker, Vagrant } \\
     \textbf{Databases}{: MySQL, PostgreSQL (learning)} \\
     \textbf{Currently Exploring}{: C/Clang, Go/Golang, Emacs Lisp } \\
     \textbf{Certifications}{: RHCE, LPIC-2, CompTIA Security+ ce, OCP MySQL 5}
    }}
 \end{itemize}
%
 %-------------CERTIFICATIONS-------------
\section{Certifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
            \textbf{RHCE}{: Red Hat Certified Engineer} $|$ \scriptsize{Certification id: 140-006-107} $|$ \tiny\href{https://rhtapps.redhat.com/verify?certId=140-006-107}{\underline{https://rhtapps.redhat.com/verify?certId=140-006-107}} \\
            \small\textbf{LPIC-2}{: Linux Professional Institute Certified 2} $|$ \scriptsize{LPI id: LPI000158356, Verification code: mb7jktkvsw} $|$ \tiny\href{https://cs.lpi.org/caf/Xamman/certification}{\underline{https://cs.lpi.org/caf/Xamman/certification}} \\
            \small\textbf{CompTIA Security+ ce}{: CompTIA Security+ ce} $|$ \scriptsize{Verification code: GQLW8VBFMPREQ4GR} $|$ \tiny\href{http://verify.CompTIA.org}{\underline{http://verify.CompTIA.org}} \\
            \small\textbf{OCA MySQL 5}{: Oracle Certified Associate, MySQL 5} $|$ \scriptsize{Oracle Testing ID: OC1317290} \\
            \small\textbf{OCP MySQL 5}{: Oracle Certified Professional, MySQL 5 DBA} $|$ \scriptsize{Oracle Testing ID: OC1317290}
        }}
 \end{itemize}

%
%COMMUNITY INVOLVEMENT & TEACHING
\section{Community Involvement \& Teaching}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
            \textbf{Speaker at Slackware Show 2010}{: "\emph{Package Installation and management in Slackware}"} $|$ \tiny{Presented at Instituto Infnet, Rio de Janeiro, Brazil, 2010} \\
            \small\textbf{Maintainer of Slackbuilds packages}{: Automation for installation of some packages for Slackware Linux} $|$ \tiny{2010-2013} \\
            \small\textbf{Linux and Information Security Teacher}{: for teenagers living in vulnerable contexts} $|$ \tiny{CEFET, by Petrobras, 2012} \\
            \small\textbf{Grammar reviewer contributor}{: of the ProGit pt-BR 1st edition} $|$ \tiny{2013} \\
            \small\textbf{IT Manager and Youth Teacher}{: managed a team of volunteers; Sunday school youth teacher} $|$ \tiny{Igreja Batista Betel de Mesquita, 2012-2017}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
