
\documentclass{harnon-cv}

	% personal details
	\author{Nilton Silva de Moura}  % OR - \yourname{My Name}
	\yournumber{+55 21 XXXXX-XXXX}
	\youraddress{Rio de Janeiro\\Brazil}
	\yourwebsite{https://linkedin.com/in/nmoura/}

	%personal statement
	\recenthistory{Engineer with almost 20 years of multi-skilled professional experiences as System Administrator, Development Engineer, DevOps and Support Analyst, looking for a challenging opportunity as an engineer to invent and simplify. \emph{Ownership and customer obsession} are his principles that stand out the most. Self-taught, everyday learner, assertive, with good team spirit, self-motivated, and able to work under pressure. Requiring minimal supervision, he can handle multiple demands and set priorities.}

	\begin{document}
	
		\maketitle
		
		% add your recent experience 'timeline'
		\addheadertext{Experience}
		\starttimeline
			\timelineitem{Jul/2021-now}{
				\addsubheader{Systems Management Specialist, Kyndryl - Rio-BRA}
                As a senior member of the team responsible for the infrastructure of the Wall Street Systems application that runs on IBM, he has been developing and implementing automation solutions with Python, Ansible and Shell scripts, mainly on Red Hat Enterprise Linux systems. He's also mentoring another engineers on a variety of technical subjects and providing last level support in high complexity issues.
			}
			\timelinespacer

			\timelineitem{Sep/18-May/21}{
				\addsubheader{Systems Development Engineer II, Amazon Web Services - Dublin-IRL}
				As owner of the software of the Console Network, an out-of-band network present in all datacenters, comprehended of approximately 100k network devices from various platforms, that provides administrative access to all network devices at AWS:\par
				\addtimelinebullet{He was the creator, principal developer and maintainer of a network discovery system to map large networks in restricted environments. This Python system allowed the Network Engineers to see, for the first time, the actual state of the Console Network, hence enabling them to design, plan and migrate it from an old layer 2 to a new layer 3 design.}
				\addtimelinebullet{Participated in the building of an Operating System based on the Linux Buildroot for a new terminal server hardware designed by our team. Developed, in Python, its CLI (Command Line Interface). This new device reduced the acquisition cost by 75\%, allowed flexibility to customize and implement features according to customer needs.}
				\addtimelinebullet{Developed a tool in Python to rotate the credentials of the Console Network devices, improving its security by avoiding manual errors and reducing the time of the rotation of an entire AWS region from several days to a few hours.}
				\addtimelinebullet{Developed a tool in Python that automated the steps of the migration of the Console Network design, reducing the time of a single DC fabric migration from 5 to 2 days.}
			}
			\timelinespacer

			\timelineitem{2017-2018}{
				\addsubheader{Senior Support Analyst, ANBIMA - Rio-BRA}
				\addtimelinebullet{Designed and implemented JBoss and Apache servers on RHEL using Ansible, applying best security practices from CIS (Center for Internet Security) for an application to serve account statement of big financial players (SELIC) on the Internet, with all components (databases, web servers and middleware servers) communicating themselves with mutual authentication and cryptography.}
				\addtimelinebullet{Led a project of Dynatrace (Application Performance Management) software implementation.}
				\addtimelinebullet{Troubleshooted high complexity issues.}
			}
			\timelinespacer

			\timelineitem{2014-2017}{
				\addsubheader{Support Analyst, ANBIMA - Rio-BRA}
				\addtimelinebullet{Wrote a standard for shell scripts development for the automated site disaster recovery. Developed standardized functions to be consumed by the shell scripts developed for the automated DR. Later, orchestrated the execution of the developed scripts using Jenkins Pipeline, reducing the time for the exchange of roles between sites from around 4h to 16m during DR exercises.}
				\addtimelinebullet{Designed and implemented a new architecture for 40 JBoss EAP instances; in the old architecture, there were 4 instances with around 10 applications each.}
				\addtimelinebullet{Implemented GitLab for code collaboration of infrastructure teams and gave Git and GitLab lessons to colleagues.}
				\addtimelinebullet{Supported the development teams in JBoss EAP 6 and CI/CD tools like Jenkins, Sonar and Selenium.}
			}
			\timelinespacer

			\timelineitem{2011-2014}{
				\addsubheader{IT Analyst, Petrobras, by Spassu Tecnologia - Rio-BRA}
				\addtimelinebullet{Supported the E\&P development teams in JBoss EAP 5 and 6, continuous integration process with Jenkins, Sonar, JIRA, Git, Subversion and Mercurial in RHEL and CentOS.}
				\addtimelinebullet{Designed and implemented the JBoss EAP 6 architecture and Spacewalk (an open-source systems management software) for all Brazil E\&P workstations and servers, based on RHEL and CentOS, automatizing Red Hat channels synchronization with Python.}
				\addtimelinebullet{Implemented a GitLab server for development and infrastructure teams.}
				\addtimelinebullet{Wrote a baseline for the VMWare virtual servers, for RHEL 6 and CentOS.}
				\addtimelinebullet{Implemented Jenkins and applications deployment with shell scripts.}
				\addtimelinebullet{Began the implementation of Puppet Open Source for servers and workstations configuration management.}
			}
			\timelinespacer

			\timelineitem{2010-2010}{
				\addsubheader{Senior Support Analyst, Equinix - Rio-BRA}
				\addtimelinebullet{Identified root causes of recurrent issues. Troubleshooted high complexity issues, mainly in Linux and its services. Supported analysts on technical questions.}
			}
			\timelinespacer

			\timelineitem{2009-2010}{
				\addsubheader{Junior Support Analyst, Equinix - Rio-BRA}
				\addtimelinebullet{Treated issues quickly enough to try to avoid breaking up SLA as first customer contact, mainly in Linux systems and its services like DNS (BIND), Web (Apache), Database (MySQL), Email (Postfix and Zimbra), Firewall (iptables), Proxy (Squid) and Shellscript.}
			}
			\timelinespacer

			\timelineitem{2008-2009}{
				\addsubheader{Operations Analyst, AMT Internet Security \& DataCenter - Rio-BRA}
				\addtimelinebullet{Responsible for design, deploy and server management, mostly in Linux environments for services like DNS (BIND and Windows 2008), Firewall (iptables), Antispam, Monitoring (Nagios), in physical and virtual servers (Citrix-Xen), acting as the last support level for customers.}
			}
			\timelinespacer

			\timelineitem{2008-2008}{
				\addsubheader{Junior Support Analyst, AMT Internet Security \& DataCenter - Rio-BRA}
				\addtimelinebullet{Monitored servers and services, treating first level issues as the first contact with customers.}
			}
			\timelinespacer

			\timelineitem{2004-2008}{
				\addsubheader{Processing Technician, HSBC Bank Brasil - Rio-BRA}
				\addtimelinebullet{Supported managers and internal clients on information management, control and management of internal flows. Managed Microsoft Access database. Optimized operational routines. Coordinated a team of research and support processes.}
			}
			\timelinespacer

			\timelineitem{2000-2001}{
				\addsubheader{Webdeveloper/Webdesigner, Editora Graça - Rio-BRA}
				\addtimelinebullet{Developed and maintained the first website of a magazine in pure HTML. Technically supported colleagues.}
			}
			\timelinespacer

		\stoptimeline

		\addheadertext{Formal Education}
			\starttimeline
				\timelineitem{2022-2023}{
				\addsubheader{MBA in Software Engineering, UFRJ (Rio de Janeiro's Federal University)}
				\tiny Expected completion in mid-2023
			}
			\timelinespacer
			\starttimeline
				\timelineitem{2009-2011}{
				\addsubheader{Tech. Degree in Computer Networks, UGF (Gama Filho University)}
				\tiny Grade: 8.8
			}
			\timelinespacer
			\starttimeline
				\timelineitem{2000-2002}{
				\addsubheader{High School specialized in Technical IT, Colégio Nacional}
				\tiny Selected by school's direction to join the first Advanced Studies Group
			}
			\timelinespacer

		\addheadertext{Relevant Certifications}
		\begin{flushleft}
			\begin{multicols}{2}
				\addsubheader{CompTIA Security+ ce}
				\tiny{\href{http://verify.comptia.org/}{Verification Code: GQLW8VBFMPREQ4GR, ID: COMP001021234924}}\\
				\addsubheader{RHCE - Red Hat Certified Engineer}
				\tiny{\href{https://rhtapps.redhat.com/verify?certId=140-006-107}{License: 140-006-107}}\\
			\end{multicols}
			\begin{multicols}{2}
				\addsubheader{Oracle Certified Associate, MySQL 5}
				\tiny{ID: SUN629015}\\
				\addsubheader{Oracle Certified Professional, MySQL 5 DBA}
				\tiny{ID: SUN629015}\\
			\end{multicols}
		\end{flushleft}

        \clearpage
		\addheadertext{Community Contributions \& Volunteering}
			\addsubheader{Individual Contributor, Stack Overflow, 2022-now}
			\tiny {\href{https://stackoverflow.com/users/11265847/nilton-moura}{Nilton Moura's Profile}\\

			\addsubheader{IT Manager at Igreja Batista Betel de Mesquita, 2012-2017}
			\tiny Management of a team of volunteers, prospection and implementation of technologies, etc.\\

			\addsubheader{Maintainer of some Slackbuilds packages, 2010-2013}
			\tiny Automation for installation of some packages that were not officially distribuited within the Slackware Linux.\\

			\addsubheader{Linux and Security Teacher, CEFET, by Petrobras, 2012}
			\tiny For young people who could not afford to pay a good course to prepare them for the job market.\\

			\addsubheader{Speaker at Slackware Show 2010, Instituto Infnet, Rio de Janeiro, Brazil, 2010}
			\tiny Subject: \emph{Package Installation and Management in Slackware}.\\

		\addheadertext{Languages}
			\addsubheader{English (Advanced) and Portuguese (Native)}

	\end{document}
